---
title: "EODPlotter manual"
author: "Colin Diesh"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# EODPlotter User Manual

## Source Code

https://github.com/msuefishlab/eodplotter

## Installation

EODPlotter is designed as an R package, to be installed using a package
manager. EODPlotter is a command line alternative to the [TDMSViewer](https://github.com/msuefishlab/tdmsviewer)

We will install EODPlotter from github. Open RStudio and run

```{r,eval = FALSE}
install.packages('devtools')
```

This will install the devtools package which has the `install_github` function. Then run

```{r,eval = FALSE}
devtools::install_github('msuefishlab/eodplotter')
```

After running this it should install the EODViewer code and its
dependencies automatically. 

To install a specific version, e.g. the version mentioned in this guide, you
can also run

```{r,eval = FALSE}
install_github('msuefishlab/eodplotter@0.0.2')
```
## Using EODPlotter

Once the library is installed, you can use it using either


- Command line
- On R interactive prompt
  
### Using the command line

Todo

### Using the R library directly

Todo
