---
title: "EODPlotter manual"
author: "Colin Diesh"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# EODPlotter User Manual

## Source Code

https://github.com/msuefishlab/eodplotter

## Installation

EODPlotter is designed as an R package, to be installed using a package
manager. EODPlotter is a command line alternative to the [TDMSViewer](https://github.com/msuefishlab/tdmsviewer)

We will install EODPlotter from github. Open RStudio and run

```{r,eval=F}
install.packages('devtools')
```

This will install the devtools package which has the `install_github` function. Then run

```{r,eval=F}
devtools::install_github('msuefishlab/eodplotter')
```

After running this it should install the EODViewer code and its
dependencies automatically. 

To install a specific version, e.g. the version mentioned in this guide, you
can also run

```{r,eval=F}
install_github('msuefishlab/eodplotter@0.0.2')
```
## Using EODPlotter


Plot the raw signal of the data using plotTdms

```{r}
library(eodplotter)
plotTdms('../tests/testthat/file.tdms')
```

Find peaks

```{r}
p = peakFinder('../tests/testthat/file.tdms')
library(xtable)
xtable(head(p))
```

Get a matrix of EOD signal

```{r}
m = getEODMatrix('../tests/testthat/file.tdms', p)
xtable(head(m))
```

Plot the matrix of EOD signals

```{r}
plotAverage(m)
```



Plot all the signals

```{r}
plotTotal(m)
```



Plot the matrix of EOD signals

```{r}
landmarks = findLandmarks(m)
xtable(landmarks)
```


Plot the landmarks

```{r}
plotLandmarks(m, landmarks)
```


Get stats about the landmarks

```{r}
getStats(p, landmarks)
```


## Conclusion


This demo shows you how to use the `eodplotter` as an R library. Note that there is the alternative usage of the library using the command line as well, which can be more streamlined
